### 2017-11-11 Graduate - Introduction to Analysis I/Assignment 7/7-Homework20171108.tex
add prob 1
add prob 3

Necessity. With the definition of outer measure, for each $\epsilon_n = \epsilon{1}{2^n} $, there exist an open set $O_n = \bigcup\limits_{j=1}^{\infty}I_{n_j} $ being the construction of open intervals, s.t. $E\subset O_n $, and $m(O_n) = \sum\limits_{j=1}^{\infty}m(I_{n_j}) < \epsilon_n $. Let $\{I_n\} = \{I_{n_j}\}_{n, j} $, then for each $x\in E$, $x$ belongs to infinitely many of these open intervals, and $\sum\limits_{n=1}^{\infty}m(I_n) = \epsilon < \infty$.
% Let $\mathcal{F} = \bigcup O_k $, where $O_k = \bigcup I_{k_j} $ is an open set covering $E$. Then since $E$ is a set of outer measure 0, for each $\epsilon > 0$, there exists $O_k $, s.t. $O_k \supset E $ and $m(O_k) < \epsilon$. Then for each $x\in E$, $x\in O_k \in \mathcal{F}$. This means $\mathcal{F}$ is a (general) Vitali cover of $E$. By Problem 6.6 (Gereral case of Vitali covering lemma), for $\epsilon_n = \frac{\epsilon}{2^n}$, there exists

\bigskip
\item  Problem 10, Chapter 6
\item  Problem 13, Chapter 6

>>>>

Necessity. With the definition of outer measure, for each $\epsilon_n = \epsilon{1}{2^n} $, there exist an open set $O_n = \bigcup\limits_{j=1}^{\infty}I_{n_j} $ being the construction of open intervals, s.t. $E\subset O_n $, and $m(O_n) = \sum\limits_{j=1}^{\infty}m(I_{n_j}) < \epsilon_n $. Let $\{I_n\} = \{I_{n_j}\}_{n, j} $, then for each $x\in E$, $x$ belongs to infinitely many of these open intervals, and $\sum\limits_{n=1}^{\infty}m(I_n) = \epsilon < \infty$.

\bigskip
\item  Problem 10, Chapter 6

\smallskip
\textbf{Solution:}
\smallskip
For $x_2 > x_1 $, 
$$
\begin{aligned}
f(x_2) &= \sum_{k=1}^{\infty}l((c_k, d_k)\cap (-\infty, x_2)) = \sum_{k=1}^{\infty}l((c_k, d_k)\cap (-\infty, x_1)) + l((c_k, d_k)\cap (x_1, x_2)) \\
&= f(x_1) + \sum_{k=1}^{\infty}l((c_k, d_k)\cap (x_1, x_2)).
\end{aligned}
$$
Since $(c_k, d_k)$ is an open set, and $\exists k$, s.t. $x_1\in(c_k, d_k) $, thus $l((x_1, x_2)\cup (c_k, d_k)) > 0$. So $f(x_2) > f(x_1)$, which means $f$ is increasing.

$\forall x\in E$, let $\{k_i\}$ be the infininte set where $x \in (c_{k_i}, d_{k_i})$. Let $f_k(x) = l((c_k, d_k) \cap (-\infty, x))$, then $f = \sum f_k $. Fix an $N > 0$, then since $x\in\bigcap\limits_{i=1}^{N}(c_{k_i}, d_{k_i}) $, and the intersection of finite open sets is also an open set, then there exists $t_N > 0 $, s.t. $x+t_N \in\bigcap\limits_{i=1}^{N}(c_{k_i}, d_{k_i}) $. Thus 
$$
f_k(x+t_N)-f_k(x) = l(x, x+t_N) = t_N,
$$
for each $k = k_i, 1\le i\le N$. Thus since each $f_k$ is nondecreasing, $f(x+t_N) - f(x) \ge Nt_N$, we have $\overline{D}f(x) \ge N$. With the arbitrariness of $N > 0$, we know $\overline{D}f(x) = \infty$, which means $f$ is not differentiable at $x$.

\bigskip
\item  Problem 13, Chapter 6
